---
title: "Functions explained - look up alert information"
author: "Yu- Ting Cheng"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Function explained - look up alert information}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
```{r include=FALSE}
devtools::install_github("ytingc/rCTA")
library(rCTA)

```
This vignette covers how to use function `get_alert()` and `alertstat()` in the `rCTA` package. They allow users to look up real-time and detailed information of alerts and get an overview of the current bus services.  

## Look up Alerts

Function `get_alert()` allows to get detailed information about current alerts, which is helpful for schedule traveling. The following example shows how to get the alert information of bus number 8:
```{r}
result <-get_alert(bus = 8)
knitr::kable(head(result))
```

## Statistics of Alerts
Function `alertstat()` allows to obtain an overview of current alerts of all CTA buses through a summary table that provide the count of each type of alerts. 


```{r}
result <- alertstat()
knitr::kable(head(result), col.names = c("Type", "Frequency"))
```


